At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families - Supporting Information

### 2019-11-22 manuscript/reply_to_referees_2.tex

		\textbf{R:} Does the Referee really mean to suggest that plants in the same genus are less closely-related than plants in different families? Without some sources to substantiate this, we find this claim very far-fetched!

	30. Another demand to discuss intimacy [[possibly addressable, since we did add a tiny reference in intro]]

@@

		\begin{refquote}
			361-365. How interaction intimacy may explain your results? Please, discuss your results in light of the interplay between interaction type (pollination, herbivory) and intimacy (see Hembry et al. 2018).
		\end{refquote}

		\textbf{R:}

\clearpage

{\Large \bf Reply to Referee 3} [[Still to do: title, add a bit about how this could be relevant for conservation.]]

@@

	1. Title is confusing

		\begin{refquote}
			Title is confusing – difficult to pick out key message. And given that your analyses broadly give support for effects of phylogenetic distance on niche overlap, why not focus on this message, rather than variability at among individual networks/plant families
		\end{refquote}

		\textbf{R:}

	2. Request to state that networks are qualitative rather than quantitative [[done]]

		\textbf{R:} The Referee is correct that the difference between qualitative and quantitative networks is crucial for the correct ecological interpretation of said networks. We thank them for pointing out that the distinction wasn't clear in the previous version. We now specify that our networks are qualitative at the beginning of the methods and results and the end of the discussion. We hope that these few reminders will be enough to remind readers about the structure of our networks.

		Lines XX-XX (methods):

		\begin{quotation}

			All networks were qualitative, recording the presence or 
		    absence of interactions rather than their strength.

		\end{quotation}

		Lines XX-XX (results):

		\begin{quotation}

			Note that, as our networks 
		    are qualitative, these results refer only to the number of shared interaction
	    	partners rather than to the quantitative strength of competition.

    	\end{quotation}

    	Lines XX-XX (discussion):

    	\begin{quotation}

		  Although here we considered only the presence or absence of interactions,
		  (i.e., qualitative networks)

    	\end{quotation}

	3. L298 – Please be careful with use of “lesser/greater” “more negative or positive than expected from permuted networks” [[done]]

		\textbf{R:} We appreciate that this desceription could be unclear, and have revised this line as suggested. It now reads:

		Lines XX-XX:

		\begin{quotation}

			the observed 
		    slope of the relationship between phylogenetic distance and interaction 
		    partner overlap was always more extreme (i.e., always more negative or 
		    always more positive) than that obtained in the permuted networks (Fig. 2).

	    \end{quotation}

	4. Typo in line 322 [[done]]

@@

		\begin{refquote}
			L322 – how was this result obtained if insect phylogenies were not caclculated? Do you mean “more closely-related plants in pollinator networks”?
		\end{refquote}

		\textbf{R:} The Referee is correct and we apologize for this extremely confusing typo. We have corrected this line as suggested.

@@

{\Large \bf Reply to Referee 4}

	\begin{refquote}
		Understanding what drives the structure of networks of interactions is key to predict the structure of plant-insect communities (e.g., for conservation or restoration purposes, or to support benefit organisms in agriculture).
		The present study focuses on the contribution of the evolutionary history to the interaction structure, and makes a significant contribution to the understanding of the variability of the phylogenetic signal in plant-insect networks. Here, the strength of the phylogenetic signal is actually quantified while it usually relies on correlation scores, and the effect of plant composition and the identity of plant families are examined to assess whether they could explain the variability of trends described in the literature.
		The dense writing turns out to be a double-edge sword: a lot of information on drivers of phylogenetic signals is compiled in here, but the text is sometime hard to follow. Hence, my following comments mostly pertains to the form, and I trust the authors should be able to address them fairly easily.
	\end{refquote}

	\textbf{R:} We thank the Referee for their compliments to our analysis and for taking the time to review our manuscript. We appreciate that our writing can be dense at times and appreciate the Referee pointing out places where we may clarify our prose. Below, we respond to each comment in detail (preceded by \textbf{R:}). We are confident that revising the manuscript in response to the Referee's comments has improved the manuscript.

1. Confusion about description of two dependent variables in analyses

	\begin{refquote}
		* Modelling the relationship between niche overlap and phylogenetic distance
		I did not managed to fully grasp the statistical analysis right away (I reckon I'm not a statistical master, but this may be the case of other readers), and I think it was mostly due to the way the methods are described. The writing is nice, but some tiny details are missing while they could help the reader to understand more quickly how the authors distinguish the use of the {M_ij, U_ij}-tuple from that of J_ij.
		Based on l. 143-167, I understand that the number of shared interactions M_ij is modelled with a binomial distribution, with the number of trials being M_ij+U_ij, and the probability of success being w_ij (M_ij ~ B(M_ij + U_ij, w_ij)). The {M_ij, U_ij}-tuple would appear in R as follows:
		model ← glm(cbind(M_ij, M_ij+U_ij) ~ d_ij + ..., family = “binomial”)
		But, can we actually say that there are two dependent variables? To me, it is the number of shared interactions that is modelled as a binomial process, not both the number of shared and unshared interactions.

	\textbf{R:} The number of shared and unshared interactions are both dependent variables included in the analysis. The number of shared variables is indeed the key variable, but the number of unshared interactions is also important as it indicates how extraordinary a particular number of shared interactions is. The binomial process incorportates both quantities; converting the numbers of shared and unshared interactions to a proportion and weighting the observations by the total number of interactions. [[Need to address this in the text]]

2. Request to state that we use the Jaccard index more explicitly [[done]]

	\begin{refquote}
		I suppose that the analysis described in paragraph starting from l. 168 corresponds to actually modelling the Jaccard index (J_ij ~ ...). If this is right, I think this should be specified in the second paragraph (no direct mention of the Jaccard index is currently made, except the proportion l. 170 between brackets although it is not exactly written as in eq. (1)), while in the first paragraph, an equation should specify that M_ij ~ B(M_ij + U_ij, w_ij)).
	\end{refquote}

	\textbf{R:} Yes, this analysis is also using a Jaccard index, but we see how the previous version did not make this clear. We now state that both the tuple and proportional glm's use Jaccard dissimilarity. We also re-iterate the logic behind the tuple-based formulation in this paragraph.

		Lines XX-XX:

		\begin{quotation}

			To demonstrate the power of defining $\omega_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$, we repeated the above analyses using a Jaccard index based only on the proportion of interaction partners that are shared (i.e., $\omega_{ij}$ = $M_{ij}$/[$M_{ij}+U_{ij}$]). Note that while the proportion of shared interaction partners is the same in both cases, the tuple formulation gives more weight to plants with many interaction partners as these provide more information. When comparing the two approaches 
		    we observed similar trends but, notably, the tuple definition of $\omega_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 2}). We therefore show only the results when defining $\omega_{ij}$ as a tuple in the main text.

		\end{quotation}

3. Request to make non-independence of species within each community explicit. [[done]]

	\begin{refquote}
		Another point pertains to the definition of “trials” in the binomial-distributed process. If I get it right, these correspond to the union of species i and j interactions (of size P_i + P_j -2M_ij = M_ij + U_ij). However, these are not independent for reasons highlighted in the introduction (e.g., competition, facilitation between plants and/or insects). This may question the robustness of the analysis, but testing the effect of the plant community composition (negative) allows to verify this. This should be specified, I think.
	\end{refquote}

	\textbf{R:} We actually address the non-independence of trials (pairs of plants) by calculating $p$-values based on permutations of the observed networks (as opposed to assuming independent, binomially-distributed trials, which is certainly not the case). To emphasize our explanation of this, we have reordered the text and placed our discussion of the permutation methods under the sub-heading 'accounting for non-independence'. We hope that this will calm reader's worries about the validity of our conclusions.

4. Permuting the permuted networks is confusing

	\begin{refquote}
		* Evaluating type I and type II errors: Permutations of permutations
		Paragraph p. 10, l. 187-197 is a bit confusing because of phrasings such as “permutations/permuting of the permuted networks”. I don't have a better way to name this second round of permutations, but the overall is difficult to follow and could be shortened while still conveying the same message.
		Actually, I find the comment in Supplementary information 3 clearer, although no reference to Supplementary information 3 is made.
		Besides, as slopes of regressions in permuted networks are tightly grouped around zero (Fig. 2, thin lines indicating 
		extrema of slopes distribution overlapping each other), so type II errors do not seem to be a big problem here.
	\end{refquote}

	\textbf{R:} We agree with the Referee about the difficulty of describing this procedure. [[Can I just swap in whatever is in S3?]] Despite the difficulty in describing our process for finding type II error verbally, we are pleased that the Referee found the end result (Fig. 2) interpretable. [[Maybe I can move all of the type II error testing to SI?]]

5. Suggestion to consider phylogenetic diversity instead of number of plant pairs

	\begin{refquote}
		* Testing the effect of network size on the existence of a phylogenetic signal
		Here, it is specifically the number of plant pairs that is studied. I wonder whether the phylogenetic diversity of plants would not be more adapted here. Is it overlooked because similar among networks?
		I think knowing more about this effect would further illuminate why the strength of the phylogenetic signal varies between networks and would be complementary to the analysis testing the effect of plant community composition.
	\end{refquote}

	\textbf{R:} Umm... what does this mean? [[Probably going to go with "beyond the scope"]]

6. Request for consideration of multiple testing

	\begin{refquote}
		* Testing within-family existence of a phylogenetic signal
		Examining the strength of phylogenetic signal within plant families is an interesting idea. However, this leads to multiple testing which is prone to type I errors and I could not find mention of correction for this multiple testing in the text. There are actually high chances that there is at least one significant test in each table (1 – (1 – alpha)^N = 0.36 and 0.91 respectively, alpha = 0.05). Yet, the authors can indicate that there are low chances to have that many significant phylogenetic signals (using the probability mass function of the Binomial distribution, see Moran 2003 in Oikos).
	\end{refquote}

	\textbf{R:} [[Wasn't this the point of looking at type I errors? Or something?]]

7. Suggestion to mention sampling completeness as a potential explanation for specialists (discussion)

	\begin{refquote}
		On the effect of specialist pollinators

		I think that Reviewer #3 made an interesting remark on specialist pollinators, and I agree with the authors on the impossibility to assess sampling completeness on the network of this database. However, I think this should be mentioned in the text, at least to invite future works to provide their sampling effort when publishing new empirical data (hence, helping to improve future analyses).
	\end{refquote}

8. Discussion of potential tradeoffs between interactions could be sharpened (discussion)

	\begin{refquote}
		On plant families involved in different types of interactions

		p. 19-20, l. 432-448: This paragraph on systems for which both pollination and herbivory were sampled is a bit fuzzy. Talking about how diverse types of interactions can work together is a nice way to bring back the study to a broader context, though.
		First, I think the sentence of simultaneous selection pressure of pollination and herbivory could be a bit clarified (l. 439-442, “Plants may not be able to respond (…).”). Strauss & Whitthall’s chapter in the book “Ecology and evolution of flowers” gives a good insight on how these selection pressures can act together or antagonistically in shaping plants phenotypes (and eventually interactions, although not specifically discussed in their chapter).
		Second, the structure of interaction patterns could be discussed with more references than Sauve et al. (2016). Astegiano et al. (2017) make an interesting point on the asymmetry of interaction patterns in such systems (using Pearse and Altermatt (2011)’s data on Lepidotera diet, and citing the Norwood farm data set of Pocock et al. 2012, and the Donana network in Melian et al. 2009).
		Finally, the existence dynamical drivers of the structure of pollination and herbivory is mentioned. Sauve et al. (2014, 2016) indeed suggest that the way pollination and herbivory are distributed on the plant community may matter for community stability, and they studied one case where this structure is indeed not random. Yet, they do not say that these communities should be more stable (compared to which ones since plants undergo both herbivory and pollination in nature?). Whether the interconnection structure arises because it provides greater stability (as discussed by Sauve et al. 2016), or as a by-product of the assembly process (Maynard et al. 2018, Ecol. Lett.) remains to be discussed for networks combining different types of networks.
		Despite the length of this last comment, I don’t mean that the authors should develop proportionally this paragraph, but rather sharpen it.
	\end{refquote}

	\textbf{R:} - merging interaction types is a good way to bring back to broader context :) - line 439-442 could be clarified based on Strauss & Whitthall (if I can find it) - more references for structure of interaction patterns: e.g., Astegiano et al. - be more tentative for dynamical drivers (apparently Sauve et al. don't really discuss stability). Could be a by-product of assembly process (Maynard et al., 2018)

@@

	\textbf{R:} - merging interaction types is a good way to bring back to broader context :) - line 439-442 could be clarified based on Strauss & Whitthall (if I can find it) - more references for structure of interaction patterns: e.g., Astegiano et al. - be more tentative for dynamical drivers (apparently Sauve et al. don't really discuss stability). Could be a by-product of assembly process (Maynard et al., 2018)

Minor comments

9. Request for additional detail in summary point 2 [[done]]

	\begin{refquote}
		In the abstract, item 2 « shared and unshared interactions »: if it does not breach the word limit, I think a few words specifying why this is important would better showcase the study, and help to understand how it contributes to the study novelty.
	\end{refquote}

	\textbf{R:} We appreciate the Referee's suggestion. Although we did not have much room to expand the summary, we have added a short parenthetical explanation of why considering both shared and unshared partners is helpful. This point now reads:

	\begin{quotation}

		\item We quantify overlap of interaction partners for all pairs of plants in 59 pollination and 11 herbivory networks based on the numbers of shared and unshared interaction partners (thereby capturing both proportional and absolute overlap). We test 1) for relationships between phylogenetic distance and partner overlap within each network, 2) whether these relationships varied with the composition of the plant community, and 3) whether well-represented plant families showed different relationships.

	\end{quotation}

10. Incorrect referencing of Sauve et al., 2016 [[done]]

	\begin{refquote}
		p.3, l. 1-2, citation of Sauve et al. 2016 (Ecology) to say that interactions between plants and animals are critical to plants’ life cycle. I’m not sure this is the best pick as Sauve et al. rather look at how pollination and herbivory interactions are distributed in the plant community and how it may affect community stability. The following references are adequate though.
	\end{refquote}

	\textbf{R:} We have removed this reference as suggested.

11. Possible typo in page 3, lines 9-10 [[done]]

	\begin{refquote}
		p. 3, l. 9-10 « A plant’s traits are also (...) », I think there is a typo here. Shouldn’t « a » be removed ?
	\end{refquote}

	\textbf{R:} We do not believe that the original formulation was incorrect, but agree that it was inelegant. We have revised this line to read:
	\begin{quotation}
		Plant traits are also likely to determine \emph{which} specific pollinators and herbivores interact with a particular plant.
  	\end{quotation}
  	We hope that this revised version reads better.

12. ?Suggestion to remove long list of citations in lines 22-25? [[done]]

	\begin{refquote}
		p. 3, l. 22-25 : There is a lot of citations here. I agree they all point to « mixed results » but this pertains to different aspects of phylogenetic signal. Some highlight differences between mutualistic and antagonistic systems, other rather focus on difference of phylogenetic signal between trophic levels, or even focus on subset of interaction networks. I think, it would be more relevant to the reader to cite these different works to explain how mixed results are (as done in the text following this long citation list).
	\end{refquote}

	\textbf{R:} We had intended these citations to showcase a selection of researchers addressing different aspectsof phylogenetic signal, but appreciate how including them all together could be confusing. We have removed the large list so as not to distract from the more specific citations in subsequent lines.

11. Better showcase sentence on page 5, lines 78 [[done]]

	\begin{refquote}
		p. 5, l. 78 « a pairwise perspective » : This contributes to the manuscript novelty. Maybe this should be further specified?
	\end{refquote}

	\textbf{R:} We thank the Referee for noticing this line, and have added a bit more detail as to how this pairwise perspective allows us to consider both whole-network trends and trends within families.

	Lines XX-XX:

	\begin{quotation}

		Whereas previous 
	  studies have focused on the presence or absence of phylogenetic
	  signal across entire networks, we take a pairwise perspective in
	  order to obtain a more detailed picture of how plant phylogeny
	  relates to network structure. This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales.

	\end{quotation}

12. Suggestion to make a figure showing distribution of webs, or at least to add countries to the list in SI [[done]]

	\begin{refquote}
		p. 6, l. 89-90 « These networks span a range of biomes (…). » In supporting information, the countries are not indicated in the list. Alternatively, and to emphasize on the title following Reviewer #2 suggestion in the previous round of review, a figure showing the spatial distributions of the 59 + 11 network on a world map would be welcome here.
	\end{refquote}

	\textbf{R:} We have added the countries or regions (e.g., islands associated with mainland countries, such as Greenland and Denmark) to Table 1 in the SI. We hope that this will provide enough clarification about the spatial scale of our dataset. For readers who are interested, we now refer both to the original sources and from an online database (the Web of Life dataset) which collects the pollination networks we used. These sources can be used to obtain more exact coordinates.

13. Suggestions to clarify explanation of regressions [[done?]]

	\begin{refquote}
		p. 7, l. 125-141 : I think the beginning of this section should be more straightforward and contrast better the information provided by M_ij and U_ij (starting with them) with that of the Jaccard index J_ij. In addition, J_ij is never mentioned again as such (but is an estimate of w_ij).
	\end{refquote}

	\textbf{R:} We have reworded this section in an attempt to clarify the relationships between $M_{ij}$, $U_{ij}$, and $J_{ij}$ and better contrast the information given by each value. We have also changed all $\omega_{ij}$ to $J_{ij}$ for simplicity. This paragraph now reads:

### 2019-11-22 manuscript/reply_to_referees_2.tex

	\begin{quotation}
	    We calculated niche overlap for each pair of plants $i$ and $j$ by 
	    combining the number of shared interaction
	    partners ($M_{ij}$) and the number of interaction partners which are not
	    shared ($U_{ij}$) into a Jaccard index ($J_{ij}$) describing 
	    the proportion of shared interactions. Importantly, we do this while 
	    preserving the amount of information provided by each pair of plants
	    (indicated by their numbers of interaction partners). $J_{ij}$ is usually defined as: 
	    %
	    \begin{equation}
	      J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
	    \end{equation}
	    %
	    where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
	    species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
	    \emph{partners} for species $i$ and $j$ respectively. $J_{ij}$ can also be defined:
	    %
	    \begin{equation}
	      J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
	    \end{equation}
	    %
	    since $U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$. This second definition more closely
	    relates to our methodology, which used the tuple ($M_{ij}$, $U_{ij}$) as the
	    dependent variable rather than the single value $J_{ij}$. Using this tuple form
	    allows us to give more 
	    weight to species sharing a large number of interaction partners as well as 
	    those sharing a large proportion (i.e., to emphasise pairs of generalists 
	    sharing most of their interaction partners over specialists sharing a single 
	    interaction partner). Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large. % Added because Josh got confused about the distinction.
	    \end{quotation}

14. R4 has identified the source of R2's confusion about whether we permuted interactions or phylogenetic distances!

	\begin{refquote}
		p. 14, l. 297-298 “Comparing the results in the observed networks with those obtained after permuting phylogenetic distances across pairs of plants (...)”: In the methods, interactions are shuffled, not phylogenetic distances. Doing one of the other seems equivalent for this test, but this rephrasing is a bit confusing.
	\end{refquote}

15. Typo in page 15, lines 322-324 [[done]]

	\begin{refquote}
		p. 15, l. 322-324 “ More closely-related pollinators did, however, tend to share fewer interaction partners (…).”: This is the first time that conservatism of interactions is checked from the pollinators perspective in the manuscript. Is it a typo or did I miss something in the manuscript?
	\end{refquote}

	\textbf{R:} Yes, this is indeed a typo. We did not have information on pollinator phylogenies and did not test anything from the pollinator perspective. We thank the Referee for pointing this out, and have corrected the line. The sentence now reads:

	Lines XX-XX:
	\begin{quotation}
		More closely-related plants in pollination networks did, however, tend to share fewer interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
	\end{quotation}

16. Fig. 3, Table 2 conflict for Poaceae

	\begin{refquote}
		Legend of Fig. 3 “(…) Melastomatoaceae and Poaceae in pollination networks are not significantly different from zero.” but Table 2 shows the opposite for Poaceae.
	\end{refquote}

17. A confusing attempt at subtelty

	\begin{refquote}
		In the figures, \beta_distance is alternatively named “slope of regression line” (Fig. 2) and “change in log odds” (Fig. 3).
	\end{refquote}

	\textbf{R:} I think this was intentional since both interpretations apply ... but this appears to have caused some confusion. Oops.

% References

% Altermatt, F. and Pearse, I.S., 2011. Similarity and specialization of the larval versus adult diet of European butterflies and moths. The American Naturalist, 178(3), pp.372-382.

% Astegiano, J., Altermatt, F. and Massol, F., 2017. Disentangling the co-structure of multilayer interaction networks: degree distribution and module composition in two-layer bipartite networks. Scientific reports, 7(1), p.15465.

% Maynard, D.S., Serván, C.A. and Allesina, S., 2018. Network spandrels reflect ecological assembly. Ecology letters, 21(3), pp.324-334.

% Melián, C.J., Bascompte, J., Jordano, P. and Krivan, V., 2009. Diversity in a complex ecological network with two interaction types. Oikos, 118(1), pp.122-130.

% Moran, M.D., 2003. Arguments for rejecting the sequential Bonferroni in ecological studies. Oikos, 100(2), pp.403-405.

% Strauss, S.Y. and Whittall, J.B., 2006. Non-pollinator agents of selection on floral traits. Ecology and evolution of flowers, pp.120-138.
